\problemname{Pizza Problems}

\illustration{0.5}{bigpizza}{\href{https://secure.flickr.com/photos/bfsminid/4107752201/in/photostream/}{Photo} by Sam DeLong}

\noindent
Me and my friends are ordering a big pizza to share.  As you can
imagine this is quite complicated, since everyone has different wishes
about what should be on the pizza.  For instance Gunnar wants bananas
on the pizza, Emma doesn't want bananas but wants olives, Marc wants
there to be tomatoes, and so on.  Fortunately, against all odds, we
managed to come up with a selection of toppings such that everyone had
at least $2/3$'s of their wishes fulfilled, which we unanimously decided was
good enough.

But then, disaster struck!  We sent out Lukáš to buy the pizza, but he
accidentally lost the piece of paper on which we had written down our
carefully selected list of toppings.  Now we're back at square one,
and have to construct a new selection of toppings.  Given how long it
took us to find the original selection of toppings, we have decided to
lower our standards a bit and just try to find a selection such that
everyone has \emph{strictly} more than $1/3$ of their wishes fulfilled.

Can you help us with this?  If you do, you'll get some pizza!


\section*{Input}

The first line of input contains an integer $1 \le N \le 10\,000$, the
number of friends in the group (including yourself).  Each of the next
$n$ lines contains the list of wishes of one of the friends.  This
list starts with an integer $1 \le w \le 30$, the number of wishes
this friend has, followed by a space-separated list of wishes.  Each
wish is either ``\texttt{+<topping>}'' or ``\texttt{-<topping>}''
where \texttt{<topping>} is the name of a topping, indicating that
this friend wants or does not want this topping.  Each topping name
appears at most once in each list.

Topping names are non-empty strings of up to $15$ lower-case English
letters `\texttt{a}'-`\texttt{z}'.  There are at most $250$ different toppings.

\section*{Output}

Output a list of toppings (without repetitions, separated by spaces or newlines) such that
each friend has strictly more than $1/3$ of their wishes fulfilled.  You may
assume that there exists a list such that every friend has at least $2/3$
of their wishes fulfilled.

Your list of toppings is not allowed to contain any toppings that are
not mentioned in the input, nor is it allowed to contain repetitions.
